Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-02-18 RR_manuscript/Draft_RR.tex
:art: - use pdf_document2 for now

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
  pdfauthor={First Author\#, Second Author\#, \ldots\#, \& Last Author\#},
  pdflang={en-EN},
  pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Many analysts - one speech data set}
\keywords{crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{cleveref}
\usepackage{changes}
\definechangesauthor[name={Stefano Coretta}, color=red]{SC}
\definechangesauthor[name={Timo Röttger}, color=blue]{TR}
\definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.}
\author{First Author\textsuperscript{\#}, Second Author\textsuperscript{\#}, \ldots{}\textsuperscript{\#}, \& Last Author\textsuperscript{\#}}
\date{}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Second Author: Writing - Review \& Editing; \ldots{}: Writing - Review \& Editing; Last Author: Writing - Review \& Editing.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} \#\\\textsuperscript{\ldots{}} \ldots{}}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

@@

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (Camerer et al., 2018; e.g., Open Science Collaboration, 2015) leading to what is now referred to as the \emph{replication crisis}.
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, \& Dubé, 2015; Starns et al., 2019) and is, among other things, rooted in the inherent flexibility of data analysis (Gelman \& Loken, 2014; often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011).
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g., Box, 1976; De Groot, 2014; Tukey, 1977).
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons, Nelson, \& Simonsohn, 2011).
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (Botvinik-Nezer et al., 2020; e.g., Silberzahn et al., 2018; Starns et al., 2019).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

@@

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways (e.g., Tversky \& Kahneman, 1974), seeing coherent patterns in randomness (Brugger, 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson, 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff, 1975).
In connection with an academic incentive system that rewards certain discovery processes more than others (Koole \& Lakens, 2012; Sterling, 1959), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger, 2019).
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (Gelman \& Loken, 2014; e.g., Simmons, Nelson, \& Simonsohn, 2011).
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006).

While this issue has been widely discussed both from a conceptual point of view (Nosek \& Lakens, 2014; Simmons, Nelson, \& Simonsohn, 2011; Wagenmakers, Wetzels, Borsboom, Maas, \& Kievit, 2012) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger, 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.

@@

However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question.
In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa (Flake \& Fried, 2019).
To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.

@@

Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories {[}e.g., Jongman, Wayland, and Wong (2000); Lisker (1986); Summerfield, 1984; Winter (2014){]}.
A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon \& Roettger, 2017).

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd, 2008).
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations (Van Heuven, Haan, Gussenhoven, \& Warner, 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven \& Van Zanten, 2005).
Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).

@@

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations? (e.g.~\emph{a blue banana} vs \emph{a yellow banana})?
We are interested in the acoustic profile of referring expressions.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice, 1975).
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Rubio-Fernández, 2016; Sedivy, 2003; Westerbeek, Koolen, \& Maes, 2015), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts, Maes, Noordman, \& Jansen, 2011; Paraboni, Van Deemter, \& Masthoff, 2007; Rubio-Fernández, 2016).
Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
For example, Degen, Hawkins, Graf, Kreiss, and Goodman (2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
This account, however, has mainly focused on content selection (Gatt, Gompel, Deemter, \& Krahmer, 2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.

Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g., Ladd, 2008).
Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
Intonation marks discourse-relevant referents for being new or given information to guide the listeners' interpretation of incoming messages.
In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \emph{banana} to indicate the contrastive nature of the noun.
In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \emph{yellow} to indicate the contrastive nature of the modifier.
In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.

@@

Assuming that the underlying distribution of effect sizes is normal (Knight, 2000), the standard error of \(\tau^2\) can be calculated with the formula:

@@

The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice, 1945; Sørensen, 1948).
The SDI is an index typically used in ecology research to compare species composition across sites.
For our purposes, we will treat predictors as species and individual analyses as sites.
For each pair of analyses \((X, Y)\), the SDI will be obtained using the following formula:

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
  pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=4cm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{cleveref}
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\definechangesauthor[name={Stefano Coretta}, color=red]{SC}
\definechangesauthor[name={Timo Röttger}, color=blue]{TR}
\definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.}
\author{true \and true \and true \and true}
\date{}

\begin{document}
\maketitle
\begin{abstract}
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

@@

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
\end{abstract}

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (e.g., Open Science Collaboration 2015; Camerer et al. 2018) leading to what is now referred to as the \emph{replication crisis}.
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, and Dubé 2015; Starns et al. 2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g., Box 1976; Tukey 1977; De Groot 2014).
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons, Nelson, and Simonsohn 2011).
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g., Silberzahn et al. 2018; Starns et al. 2019; Botvinik-Nezer et al. 2020).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

@@

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff 1975).
In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959; Koole and Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g., Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts et al. 2006).

While this issue has been widely discussed both from a conceptual point of view (Simmons, Nelson, and Simonsohn 2011; Wagenmakers et al. 2012; Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.

@@

However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question.
In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa (Flake and Fried 2019).
To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.

@@

Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories {[}e.g., Jongman, Wayland, and Wong (2000); Lisker (1986); Summerfield, 1984; Winter (2014){]}.
A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker 1977).
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins and Nguyen 2004).
The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon and Roettger 2017).

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd 2008).
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations (Van Heuven et al. 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven and Van Zanten 2005).
Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes and Docherty 2006; Ogden 2004; White, Payne, and Mattys 2009).

@@

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations? (e.g.~\emph{a blue banana} vs \emph{a yellow banana})?
We are interested in the acoustic profile of referring expressions.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003; Westerbeek, Koolen, and Maes 2015; Rubio-Fernández 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al. 2011; Paraboni, Van Deemter, and Masthoff 2007; Rubio-Fernández 2016).
Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
For example, Degen et al. (2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
This account, however, has mainly focused on content selection (Gatt et al. 2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.

Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g., Ladd 2008).
Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
Intonation marks discourse-relevant referents for being new or given information to guide the listeners' interpretation of incoming messages.
In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \emph{banana} to indicate the contrastive nature of the noun.
In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \emph{yellow} to indicate the contrastive nature of the modifier.
In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.

@@

Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the formula:

@@

The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice 1945; Sørensen 1948).
The SDI is an index typically used in ecology research to compare species composition across sites.
For our purposes, we will treat predictors as species and individual analyses as sites.
For each pair of analyses \((X, Y)\), the SDI will be obtained using the following formula:
